ZSE Manuscript Outline

### 2021-05-25 outline/outline.tex
changes based on Bill's comments

% Created 2021-05-13 Thu 12:16
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[version=3]{mhchem}
\usepackage[numbers,super,sort&compress]{natbib}
\usepackage{natmove}
\usepackage{url}
\usepackage{minted}
\usepackage{underscore}
\usepackage[linktocpage,pdfstartview=FitH,colorlinks,
linkcolor=blue,anchorcolor=blue,
citecolor=blue,filecolor=blue,menucolor=blue,urlcolor=blue]{hyperref}
\usepackage{attachfile}
\usepackage{geometry}
\geometry{margin=1.0in,top=.75in,bottom=.75in}
\usepackage{graphicx}
\usepackage{color}
\usepackage[numbers,super,sort&compress]{natbib}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{font=footnotesize}
\usepackage[version=3]{mhchem}
\usepackage{siunitx}
\usepackage{fancyhdr}
\usepackage{paralist}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{mdwlist}
\usepackage{hyperref}
\pagestyle{fancy}
\usepackage{wrapfig}
\usepackage{nopageno}
\fancyhf{}
\fancyhead[LE,RO]{\scriptsize Jerry Crum}
\fancyhead[RE,LO]{\scriptsize ZSE Outline}
%\fancyfoot[CE,CO]{\leftmark}
\fancyfoot[LE,RO]{\thepage}
%\usepackage{subfig}
\usepackage{comment}
\usepackage{titlesec}
\titlespacing*{\section}
{0pt}{0.6\baselineskip}{0.2\baselineskip}
\titlespacing*{\subsection}
{0pt}{0.6\baselineskip}{0.2\baselineskip}
\titlespacing*{\subsubsection}
{0pt}{0.4\baselineskip}{0.1\baselineskip}
\usepackage{parskip}
\usepackage[section]{placeins}
\usepackage{siunitx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\green}[1]{\textcolor{green}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}
\usepackage[capitalise]{cleveref}
\author{Jerry T. Crum\(^{\text{a}}\), Justin R. Crum\(^{\text{b}}\), William F. Schneider\(^{\text{a,c}}\)}
\date{}
\title{ZSE Manuscript Outline}
\begin{document}

@@

\newpage
\section*{Questions to settle with Bill:}
\label{sec:org41438e4}
\begin{enumerate}
\item Where should vertex symbol go?
\item Discuss the table and make sure we are in agreement on everything
\item Naming the ring conventions:
\begin{enumerate}
\item Goetzke: ring, primitive ring, fundamental ring \cite{marians-network-1990,guttman-ring-1990,goetzke-properties-1991}
\item Sastre: Shortest path ring, something else?
\item Crum: Unstacked rings, something else?
\end{enumerate}
\item There are other ring definitions that I have not included in this study: strong ring, and very strong ring. Should we at least introduce those in the intro?
\end{enumerate}

\section*{Highlights}
\label{sec:org6acb588}
What is the main point of the paper? What problem is it addressing? What are the main insights?

\begin{enumerate}
\item Zeolite framework creates rings, defined as closed paths with no shortcuts.
\item We provide a Python package that has the ability to find these rings based on previously published and new conventions
\item We enumerate all rings up to 18 T-sites across all known Fws using each of these conventions
\begin{enumerate}
\item Would be very cool to classify Fws according to these rings\ldots{}.
\begin{enumerate}
\item Not sure what approach to use for that, but it is a good idea
\end{enumerate}
\item Compare to other classifications, eg cage-window vs channel
\end{enumerate}
\item Various conventions for associating some subsets of these rings with either a framework or with the T-sites of a framework. Compute and compare conventions across all known frameworks.
\item Some features treated by convention as rings are not rings in a topological sense but are rather defined by the void space they create.
\end{enumerate}

\section*{Introduction}
\label{sec:orge351f77}
Introduction needs more structure.  Start with background, identify the problem you want to address.

Zeolites are microporous and crystalline, natural to characterize by the sizes of the features present in the crystal.  Rings are one common type of feature widely reported and used, both to characterize a zeolite crystal and as descriptors of the individual tetrahedral sites of the zeolite.  Provide some historical perspective here\ldots{}.
\begin{itemize}
\item Rings have been used to identify feasible zeolite topologies \cite{li-why-2014}, to descirbe the similarity and differences between zeolites \cite{curtis-statistical-2003}, to identify sites or voids of catalytic relevance \cite{li-first-principles-2018,kester-effects-2021}, and as machine learning finger prints [will get citations for this] \red{need more thorough citing}

@@

\begin{center}
\includegraphics[width=0.60\textwidth]{../figures/completed-figures/ring-examples.pdf}
\captionof{figure}{Cutout of the Chabazite framework showing a path from node 3 to node 9 outlined in teal, a cycle (3-4-18-19-20-17) outlined in red, an 8-MR in pink, and a 4-MR in green. Yellow atoms are Si (T-sites), and red atoms are oxygen. \label{fig:cha-labeled}}
\end{center}
\newpage

@@

\hline
\endhead
\hline\multicolumn{5}{r}{Continued on next page} \\
\endfoot
\endlastfoot
\hline
Nodes & T-sites and oxygen atoms & Contains some set of symmetry distinct T-sites and oxygen atoms &  & \\
Paths & Collection of connected nodes from source to target & Periodic cell contains an infinite number of paths &  & \\
Cycles & Path that starts and ends at the same node & Periodic cell Contains an infinite number of cycles &  & \\
Rings & Cycle that contains no shortcuts & Contains a finite number of unique rings & All rings that pass through particular T-site & All rings that pass through particular oxygen atom\\
Unstacked Rings & Ring that does not traverse two stacked rings & A subset of the Rings above & All unstacked rings that pass through T-site & All unstacked rings that pass through oxygen atom\\
Shortest Path Rings & Ring that is the shortest ring for at least one set of O-T-O on the cycle & A smaller subset of the rings above & All shortest path rings that pass through T-site & All shortest path rings that pass through oxygen atom\\
\red{Vertex Symbol} & Way to classify the rings around a T-site, shortest ring (and its multiplicity) for each O-O pair around a T-site & Collection of vertex symbols for all symmetry distinct T-sites in framework & Vertex symbol for particular T-site & \\
Geometric rings & A cycle that may contain a shortcut, but has similar geometric/chemical properties to a ring without a shortcut & Contains a finite number of geometric rings & Can be described by the geometric rings that pass through & Can be described by the geometric rings that pass through\\
\end{longtable}

\begin{itemize}
\item Different conventions exist that can reduce the set of rings to more strictly defined properties
\item These methods return different sets of rings
\item We can use rings to characterize oxygen atoms, T-sites, and entire frameworks
\item T-sites:
\begin{itemize}
\item Vertex symbols are the set of shortest paths connecting the 6 oxygen-oxygen pairs around a T-site \cite{okeeffe-vertex-1997}
\item Shortest path rings count all the vertex symbol rings that pass through a T-site or an oxygen atom \cite{sastre-topological-2009}
\item Or we can count all the rings that do not have a short cut \cite{goetzke-properties-1991}
\end{itemize}
\item Oxygen atoms:
\begin{itemize}
\item Shortest path rings
\item All rings with out a shortcut
\end{itemize}
\item Framework
\begin{itemize}
\item Vertex symbol rings
\item Shortest path rings
\item All rings with out a shortcut
\end{itemize}
\item Differences in ring counts leads to differences in how we describe the topology of zeolites. Therefore, when discussing the rings in a zeolite it is important to also state which method of ring counting is used.
\item Here we present Zeolite Simulation Environment (ZSE), a Python package that implements the ring finding algorithm presented by Goetzke and Klein \cite{goetzke-properties-1991} to find rings up to a user defined cutoff size, and can implement the previously published ring set reduction conventions.
\item We use ZSE to provide an analysis of rings using each of these conventions on the entire set of IZA zeolite frameworks to compare how they result in different characterizations
\end{itemize}

\red{Introduction needs to foreshadow the important insights. We captured those in your abstract. They need to appear here too.}
\section*{Software Description}
\label{sec:org97556f3}

@@

\section*{Results}
\label{sec:orgbf8efd2}
\begin{itemize}
\item Ring counts frequency plots
\begin{itemize}
\item Plot showing how many frameworks on the IZA contain each size ring found using the various ring counting methods
\item This highlights the differences in the ring rules, and shows that results will vary depending on rule.
\end{itemize}
\end{itemize}
\begin{center}
\includegraphics[width=.6\textwidth]{../figures/completed-figures/ring-counts.pdf}
\captionof{figure}{Number of IZA frameworks containing each size ring, using the various ring counting rules. [This will be updated with the Sastre method, vertex method, and the rings listed on  the IZA website. Currently the IZA does not show any ring data for the SVY framework, providing one less framework to count.  \label{fig:ring-counts}}
\end{center}

@@

\section*{Conclusions}
\label{sec:orgd035302}
\begin{itemize}
\item \red{Rings of graph are well defined; here identify all rings up to XXX in YYY frameworks. Find that commonly reported (IZA) ring sizes miss certain rings.}
\end{itemize}

@@

\section*{Acknowledgments}
\label{sec:orgc0a6c6b}
\begin{itemize}
\item Funding
\begin{itemize}
\item CISTAR
\item Schmitt Fellowship
\end{itemize}
\item Discussions
\begin{itemize}
\item Christian Baerlocher
\end{itemize}
\item Software:
\begin{itemize}
\item German Sastre: zeoTsites
\end{itemize}
\item Compute Resources
\begin{itemize}
\item CRC
\end{itemize}
\end{itemize}
\end{document}

>>>>

% Created 2021-05-25 Tue 11:13
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[version=3]{mhchem}
\usepackage[numbers,super,sort&compress]{natbib}
\usepackage{natmove}
\usepackage{url}
\usepackage{minted}
\usepackage{underscore}
\usepackage[linktocpage,pdfstartview=FitH,colorlinks,
linkcolor=blue,anchorcolor=blue,
citecolor=blue,filecolor=blue,menucolor=blue,urlcolor=blue]{hyperref}
\usepackage{attachfile}
\usepackage{geometry}
\geometry{margin=1.0in,top=.75in,bottom=.75in}
\usepackage{graphicx}
\usepackage{color}
\usepackage[numbers,super,sort&compress]{natbib}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{font=footnotesize}
\usepackage[version=3]{mhchem}
\usepackage{siunitx}
\usepackage{fancyhdr}
\usepackage{paralist}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{mdwlist}
\usepackage{hyperref}
\pagestyle{fancy}
\usepackage{wrapfig}
\usepackage{nopageno}
\fancyhf{}
\fancyhead[LE,RO]{\scriptsize Jerry Crum}
\fancyhead[RE,LO]{\scriptsize ZSE Outline}
%\fancyfoot[CE,CO]{\leftmark}
\fancyfoot[LE,RO]{\thepage}
%\usepackage{subfig}
\usepackage{comment}
\usepackage{titlesec}
\titlespacing*{\section}
{0pt}{0.6\baselineskip}{0.2\baselineskip}
\titlespacing*{\subsection}
{0pt}{0.6\baselineskip}{0.2\baselineskip}
\titlespacing*{\subsubsection}
{0pt}{0.4\baselineskip}{0.1\baselineskip}
\usepackage{parskip}
\usepackage[section]{placeins}
\usepackage{siunitx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\green}[1]{\textcolor{green}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}
\usepackage[capitalise]{cleveref}
\author{Jerry T. Crum\(^{\text{a}}\), Justin R. Crum\(^{\text{b}}\), William F. Schneider\(^{\text{a,c}}\)}
\date{}
\title{ZSE Manuscript Outline}
\begin{document}

@@

\newpage
\section*{Questions to settle with Bill:}
\label{sec:org8bf9ac1}
\begin{enumerate}
\item Discuss the table and make sure we are in agreement on everything
\item Naming the ring conventions:
\begin{enumerate}
\item Goetzke: ring, primitive ring, fundamental ring \cite{marians-network-1990,guttman-ring-1990,goetzke-properties-1991}
\item Sastre: Shortest path ring, something else?
\item Crum: Unstacked rings, something else?
\end{enumerate}
\end{enumerate}

\section*{Highlights}
\label{sec:org389b28f}
What is the main point of the paper? What problem is it addressing? What are the main insights?

\begin{enumerate}
\item Zeolite framework and nodes commonly classified in terms of rings
\item Various conventions for associating some subsets of rings with either a framework, the T-sites of a framework, or the oxygens of a framework.
\item PROBLEM TO ADDRESS: The convention used will provide different ring counts
\item SOLUTION: We provide a Python package that has the ability to identify and classify these rings based on previously published and new conventions
\item This software tool uses a node-based search procedure that takes advantage of algorithms developed for general nets
\item We compute and compare conventions across all known frameworks
\item Some features treated by convention as rings are not rings in a topological sense but are rather defined by the void space they create.
\item We enumerate all rings, defined as paths with no short-cut, up to 18 T-sites across all known Fws
\begin{enumerate}
\item Would be very cool to classify Fws according to these rings\ldots{}.
\begin{enumerate}
\item Not sure what approach to use for that, but it is a good idea
\end{enumerate}
\item Compare to other classifications, eg cage-window vs channel
\end{enumerate}
\end{enumerate}

\section*{Introduction}
\label{sec:org645e4ed}
Introduction needs more structure.  Start with background, identify the problem you want to address.

Zeolites are microporous and crystalline, natural to characterize by the sizes of the features present in the crystal.  Rings are one common type of feature widely reported and used, both to characterize a zeolite crystal and as descriptors of the individual tetrahedral sites of the zeolite.  Provide some historical perspective here\ldots{}.

\begin{itemize}
\item Rings have been used to identify feasible zeolite topologies \cite{li-why-2014}, to descirbe the similarity and differences between zeolites \cite{curtis-statistical-2003}, to identify sites or voids of catalytic relevance \cite{li-first-principles-2018,kester-effects-2021}, and as machine learning finger prints [will get citations for this] \red{need more thorough citing}

@@

\begin{center}
\includegraphics[width=0.60\textwidth]{../figures/completed-figures/ring-examples.pdf}
\captionof{figure}{Cutout of the Chabazite framework showing a path from node 3 to node 9 outlined in teal, a cycle (3-4-18-19-20-17) outlined in red, an 8-MR in pink, and a 4-MR in green. Yellow atoms are Si (T-sites), and red atoms are oxygen. \label{fig:cha-labeled}}
\end{center}

@@

\hline
\endhead
\hline\multicolumn{5}{r}{Continued on next page} \\
\endfoot
\endlastfoot
\hline
Nodes & T-sites and oxygen atoms & Contains some set of symmetry distinct T-sites and oxygen atoms &  & \\
Paths & Collection of connected nodes from source to target & Periodic cell contains an infinite number of paths &  & \\
Cycles & Path that starts and ends at the same node & Periodic cell contains an infinite number of cycles &  & \\
Rings & Cycle that contains no shortcuts & Contains a finite number of unique rings & All rings that pass through particular T-site & All rings that pass through particular oxygen atom\\
Unstacked Rings & Ring that does not traverse two stacked rings & A subset of the Rings above & All unstacked rings that pass through T-site & All unstacked rings that pass through oxygen atom\\
Shortest Path Rings & Ring that is the shortest ring for at least one set of O-T-O on the cycle & A smaller subset of the rings above & All shortest path rings starting from a T-site (Vertex) & All shortest path rings that pass through oxygen atom\\
\red{Vertex Symbol} & Way to classify the rings around a T-site, shortest ring (and its multiplicity) for each O-O pair around a T-site & Collection of vertex symbols for all symmetry distinct T-sites in framework & Vertex symbol for particular T-site & \\
Geometric rings & A cycle that may contain a shortcut, but has similar geometric/chemical properties to a ring without a shortcut & Contains a finite number of geometric rings & Can be described by the geometric rings that pass through & Can be described by the geometric rings that pass through\\
\end{longtable}

\textbf{\textbf{Problem to address}}
\begin{itemize}
\item Different conventions exist that can reduce the set of rings to more strictly defined properties
\item These methods return different sets of rings
\item We can use rings to characterize oxygen atoms, T-sites, and entire frameworks
\item T-sites:
\begin{itemize}
\item Vertex symbols are the set of shortest paths connecting the 6 oxygen-oxygen pairs around a T-site \cite{okeeffe-vertex-1997}
\item Shortest path rings count all the vertex symbol rings that pass through a T-site or an oxygen atom \cite{sastre-topological-2009}
\item Or we can count all the rings that do not have a short cut \cite{goetzke-properties-1991}
\end{itemize}
\item Oxygen atoms:
\begin{itemize}
\item Shortest path rings
\item All rings with out a shortcut
\end{itemize}
\item Framework
\begin{itemize}
\item Vertex symbol rings
\item Shortest path rings
\item All rings with out a shortcut
\end{itemize}
\item Differences in ring counts leads to differences in how we describe the topology of zeolites. Therefore, when discussing the rings in a zeolite it is important to also state which method of ring counting is used.
\end{itemize}

\textbf{\textbf{Solution to problem}}
\begin{itemize}
\item Here we present Zeolite Simulation Environment (ZSE), a Python package that implements the ring finding algorithm presented by Goetzke and Klein \cite{goetzke-properties-1991} to find rings up to a user defined cutoff size, and can implement the previously published ring set reduction conventions.
\item We use ZSE to provide an analysis of rings using each of these conventions on the entire set of IZA zeolite frameworks to compare how they result in different characterizations
\end{itemize}

\red{Introduction needs to foreshadow the important insights. We captured those in your abstract. They need to appear here too.}

Using ZSE we show the differences in framework, T-site, and oxygen ring descriptors when using the various ring counting conventions. We highlight rings that are found by these conventions but not typically discussed for a number of frameworks. We also show that the vertex symbol, a common approach used to characterize T-sites misses important parts of the stereochemistry around a T-site.

\section*{Software Description}
\label{sec:org22a9053}

@@

\section*{Results}
\label{sec:orgf799547}
\begin{itemize}
\item Ring counts frequency plots
\begin{itemize}
\item Plot showing how many frameworks on the IZA contain each size ring found using the various ring counting methods
\item This highlights the differences in the ring rules, and shows that results will vary depending on rule.
\end{itemize}
\end{itemize}
\begin{center}
\includegraphics[width=.6\textwidth]{../figures/completed-figures/ring-counts.pdf}
\captionof{figure}{Number of IZA frameworks containing each size ring, using the various ring counting rules. [This will be updated with the Sastre method, vertex method, and the rings listed on  the IZA website. Currently the IZA does not show any ring data for the SVY framework, providing one less framework to count.  \label{fig:ring-counts}}
\end{center}

@@

\section*{Conclusions}
\label{sec:org57e4218}
\begin{itemize}
\item \red{Rings of graph are well defined; here identify all rings up to XXX in YYY frameworks. Find that commonly reported (IZA) ring sizes miss certain rings.}
\end{itemize}

@@

\section*{Acknowledgments}
\label{sec:org2e68444}
\begin{itemize}
\item Funding
\begin{itemize}
\item CISTAR
\item Schmitt Fellowship
\end{itemize}
\item Discussions
\begin{itemize}
\item Christian Baerlocher
\end{itemize}
\item Software:
\begin{itemize}
\item German Sastre: zeoTsites
\end{itemize}
\item Compute Resources
\begin{itemize}
\item CRC
\end{itemize}
\end{itemize}
\end{document}
